---
title: "'List Before Last: All 2 Cues' Performance Analysis"
author: "Will Hopper"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: yes
    toc: true
    toc_depth: 2
    css: custom.css
vignette: >
  %\VignetteIndexEntry{LB4L2: All 2 Cues}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>

img {
  padding: 10px;
  border-bottom: 2px solid #000;
}

</style>
```{r setup, include=FALSE}
devtools::load_all()
library(dplyr)
library(tidyr)
library(whoppeR)
library(ggplot2)
library(grid)
library(gridExtra)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.align='center', fig.width = 8)
```

```{r}
# IV <- summary(LB4L2_final, level = "group")
bySubject_group_prac_OCprac <- summary(LB4L2_final, level = "subject")
byGroup_prac_OCprac <- summary(bySubject_group_prac_OCprac)
```

```{r difference_sem_plot, dev="svglite"}
diff_bySubject_group_prac_OCprac <- bySubject_group_prac_OCprac %>%
  filter(acc==1) %>%
  select(-acc, -N, -cell_max) %>%
  gather(key="var", value="value", p, RT_median, RT_mean, logRT_mean) %>%
  unite(condition, practice, OCpractice, sep=".") %>%
  spread(condition, value) %>%
  group_by(subject, var) %>%
  mutate_at(c("N.S", "N.T", "S.N", "T.N"),
            funs(. - N.N)) %>%
  ungroup() %>%
  select(-N.N) %>%
  gather(key="cond", value="value", N.S, N.T, S.N, T.N) %>%
  separate(cond, into = c("practice", "OCpractice"),sep = "\\.") %>%
  spread(var,value) %>%
  recode_conditions()

diff_byGroup_prac_OCprac <- diff_bySubject_group_prac_OCprac %>%
  group_by(group, practice, cue_type) %>%
  summarise_at(c("p","logRT_mean","RT_mean","RT_median"),
            funs(sem = whoppeR::sem(., na.rm=TRUE))
            )  %>%
  rename_(.dots=setNames(names(.),
                         gsub("_mean$", "", names(.))
                         )
          )

intervention <- filter(byGroup_prac_OCprac, !(practice == "N" & OCpractice == "N")) %>%
  select(group, practice, OCpractice, p, RT_mean, logRT_mean, RT_median) %>%
  recode_conditions() %>%
  left_join(diff_byGroup_prac_OCprac)

control <- filter(byGroup_prac_OCprac, practice == "N", OCpractice == "N") %>%
  select(group, practice, OCpractice, p, RT_mean, logRT_mean, RT_median) %>%
  recode_conditions() %>%
  mutate(p_sem = NA, RT_mean_sem = NA, logRT_mean_sem = NA, RT_median_sem = NA)
control <- rbind(mutate(control, cue_type = "Same Cue"),
                 mutate(control, cue_type = "Other Cue")
                 )

theme_set(theme_bw(base_size = 16) +
          theme(plot.title = element_text(hjust = .5),
                axis.title = element_text(size=12)))
acc <- ggplot(bind_rows(control,intervention),
              aes(x=group, y=p,
                  ymax = p + p_sem,
                  ymin = p - p_sem,
                  shape = practice, group=practice)) +
  geom_point(size = 2) +
  geom_line() +
  geom_errorbar(width=.15, na.rm=TRUE) +
  facet_grid(cue_type ~ .) +
  scale_x_discrete("Group",
                   limits=c("immediate","delay"),
                   labels=c("Immediate","Delay")) + 
  scale_y_continuous("Proportion Correct") +
  scale_shape_discrete(guide=FALSE) +

  ggtitle("Accuracy") + 
  theme(strip.text.y = element_blank(),
        strip.background = element_blank())

  
RT <- acc %+%
  aes(y = RT_mean,
      ymin = RT_mean - RT_mean_sem,
      ymax = RT_mean + RT_mean_sem) + 
  scale_y_continuous("Mean R.T. (seconds)") +
  scale_shape_discrete("Practice",
                       labels = c("Control","Study Practice", "Test Practice")) +
  ggtitle("Reaction Time") +
  theme(strip.text.y = element_text(angle=0,
                                    size = 18,
                                    margin = margin(l=8)),
        strip.background = element_blank(),
        legend.margin = margin(l=-90))

g <- arrangeGrob(acc, RT,
                 nrow = 1,
                 ncol = 2,
                 widths = c(.4, .6))
grid.draw(g)

# CD <- summary(LB4L2_final, level = "group", given_practice = TRUE, conditional = TRUE) 
# identical(summary(LB4L2_final, level = "group", given_practice = 1:2, conditional = TRUE), CD)
# CD_1 <- summary(LB4L2_final, level = "group", given_practice = 1, conditional = TRUE)
# CD_2 <- summary(LB4L2_final, level = "group", given_practice = 2, conditional = TRUE)
# 
# joint <- summary(LB4L2_final, level = "group", given_practice = TRUE)
# joint_1 <- summary(LB4L2_final, level = "group", given_practice = 1)
# joint_2 <- summary(LB4L2_final, level = "group", given_practice = 2)
# 
# CD_raw <- summary(LB4L2_final, level = "raw", given_practice = TRUE, conditional = TRUE)
# joint_raw <- summary(LB4L2_final, level = "raw", given_practice = TRUE)
# identical(CD_raw, joint_raw)
```

## Accuracy and RT by Experimental Condition
```{r IV, }
# IV <- summary(LB4L2_final, level = "group")
# autoplot(IV, DV = "accuracy")
# autoplot(IV, DV = "RT")
```

## Conditional Accuracy and RT
```{r conditionals}
# CD_1 <- summary(LB4L2_final, level = "group", given_practice = 1, conditional = TRUE)
# autoplot(CD_1, DV = "accuracy")
# autoplot(CD_1, DV = "RT")
```

## Joint Accuracy and RT
```{r joint}
# joint_1 <- summary(LB4L2_final, level = "group", given_practice = 1)
# autoplot(joint_1, DV = "accuracy")
# autoplot(joint_1, DV = "RT")
```

```{r}
  # transmute(subject, group,
  #           N.S.p = N.S.p - N.N.p,
  #           N.T.p = N.T.p - N.N.p,
  #           S.N.p = S.N.p - N.N.p,
  #           T.N.p = T.N.p - N.N.p,            
  #           N.S.logRT_mean = N.S.logRT_mean - N.N.logRT_mean,
  #           N.T.logRT_mean = N.T.logRT_mean - N.N.logRT_mean,
  #           S.N.logRT_mean = S.N.logRT_mean - N.N.logRT_mean,
  #           T.N.logRT_mean = T.N.logRT_mean - N.N.logRT_mean,
  #           N.S.RT_mean = N.S.RT_mean -N.N.RT_mean,
  #           N.T.RT_mean = N.T.RT_mean -N.N.RT_mean,
  #           S.N.RT_mean = S.N.RT_mean -N.N.RT_mean,
  #           T.N.RT_mean = T.N.RT_mean -N.N.RT_mean,
  #           N.S.RT_median = N.S.RT_median - N.N.RT_median,
  #           N.T.RT_median = N.T.RT_median - N.N.RT_median,
  #           S.N.RT_median = S.N.RT_median - N.N.RT_median,
  #           T.N.RT_median = T.N.RT_median - N.N.RT_median) %>%
  # gather(key="var", value="value", -subject, -group) %>%
  # separate(var, into = c("practice", "OCpractice", "var"),sep = "\\.") %>%
  # spread(var,value) %>%
  # recode_conditions()
```

## Quantile Plots
```{r quantiles, fig.height=8,fig.width = 11, include=FALSE}

calculate_quantiles <- function(data,
                                quantiles = c(.1, .3, .5, .7, .9)) {
  
  data <- group_by(data, group, practice, OCpractice)
  data <- do(data,
             data.frame(probability = quantile_points,
                        RT = quantile(.$RT,
                                      probs=quantile_points,
                                      names=FALSE)
                        )
             )
   data <- ungroup(data)
   data
}

quantile_points <- seq(.01,1,length.out = 100)
# 
# quantiles_correct <- IV_sub %>%
#   filter(final_acc == 1,
#          !is.na(RT)) %>%
#   calculate_quantiles(quantile_points) %>%
#   left_join(y = IV[IV$final_acc==1,
#                    c("group","practice","OCpractice","mean_p")],
#             by = c("group","practice","OCpractice")) %>%
#   mutate(probability = probability * mean_p) %>%
#   select(-mean_p)
# 
# practice_labels <- c(N.N = "Baseline",
#                      N.S = "Study, Other Cue",
#                      S.N = "Study, Same Cue",
#                      N.T = "Test, Other Cue",
#                      T.N = "Test, Same Cue")
# 
# capitalize <- function(string) {
#   substr(string, 1, 1) <- toupper(substr(string, 1, 1))
#   string
# }
# 
# quantile_plot <- ggplot(quantiles_correct,
#                         aes(x=RT,
#                             y=probability,
#                             color = interaction(practice, OCpractice)
#                             )
#                         ) +
#   geom_line(size=.75) +
#   facet_grid(.~ group,
#              labeller = labeller(.default = capitalize)
#              ) + 
#   scale_color_discrete(name="Condition",
#                        breaks = c("N.N","N.S","N.T","S.N","T.N"),
#                        labels = practice_labels) +
#   scale_x_continuous(breaks = 0:6,
#                      limits=c(0,6)) + 
#   theme_grey(base_size = 16)
# print(quantile_plot)
```

### Pooled Quantiles
Quantiles are calculated using all observed RT's within a condition, pooled over subjects. They conditioned based on the observed accuracy in that condition. Thus, the quantile curves terminate at the observed accuracy for a particular condition, rather than 1.

```{r pooled_quantiles, fig.height=8,fig.width = 11}
# IV_acc_pooled <- LB4L2_final %>%
#   group_by(group,practice,OCpractice) %>%
#   summarise(acc=mean(acc))
#   
# pooled_quantiles_correct <- LB4L2_final %>%
#   filter(acc == 1) %>%
#   calculate_quantiles(quantile_points) %>%
#   left_join(y = IV_acc_pooled,
#             by = c("group","practice","OCpractice")) %>%
#   mutate(probability = probability * acc) %>%
#   select(-acc)
# 
# quantile_plot %+% pooled_quantiles_correct
```
