---
title: "'List Before Last: All 2 Cues' Performance Analysis"
author: "Will Hopper"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: yes
    toc: true
    toc_depth: 2
    css: custom.css
vignette: >
  %\VignetteIndexEntry{LB4L2: All 2 Cues}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>

img {
  padding: 10px;
  border-bottom: 2px solid #000;
}

</style>
```{r setup, include=FALSE}
devtools::load_all()
library(dplyr)
library(tidyr)
library(whoppeR)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.align='center', fig.width = 8)
```

```{r tests, include=FALSE, eval=FALSE}
# IV <- summary(LB4L2_final, level = "group")
bySubject_group_prac_OCprac <- summary(LB4L2_final, level = "subject")
byGroup_prac_OCprac <- summary(bySubject_group_prac_OCprac)

# CD <- summary(LB4L2_final, level = "group", given_practice = TRUE, conditional = TRUE) 
# identical(summary(LB4L2_final, level = "group", given_practice = 1:2, conditional = TRUE), CD)
# CD_1 <- summary(LB4L2_final, level = "group", given_practice = 1, conditional = TRUE)
# CD_2 <- summary(LB4L2_final, level = "group", given_practice = 2, conditional = TRUE)
# 
# joint <- summary(LB4L2_final, level = "group", given_practice = TRUE)
# joint_1 <- summary(LB4L2_final, level = "group", given_practice = 1)
# joint_2 <- summary(LB4L2_final, level = "group", given_practice = 2)
# 
# CD_raw <- summary(LB4L2_final, level = "raw", given_practice = TRUE, conditional = TRUE)
# joint_raw <- summary(LB4L2_final, level = "raw", given_practice = TRUE)
# identical(CD_raw, joint_raw)
```

## Accuracy and RT by Experimental Condition
```{r IV, }
# IV <- summary(LB4L2_final, level = "group")
# autoplot(IV, DV = "accuracy")
# autoplot(IV, DV = "RT")
```

## Conditional Accuracy and RT
```{r conditionals}
# CD_1 <- summary(LB4L2_final, level = "group", given_practice = 1, conditional = TRUE)
# autoplot(CD_1, DV = "accuracy")
# autoplot(CD_1, DV = "RT")
```

## Joint Accuracy and RT
```{r joint}
# joint_1 <- summary(LB4L2_final, level = "group", given_practice = 1)
# autoplot(joint_1, DV = "accuracy")
# autoplot(joint_1, DV = "RT")
```


## Quantile Plots
```{r quantiles, fig.height=8,fig.width = 11, include=FALSE}

calculate_quantiles <- function(data,
                                quantiles = c(.1, .3, .5, .7, .9)) {
  
  data <- group_by(data, group, practice, OCpractice)
  data <- do(data,
             data.frame(probability = quantile_points,
                        RT = quantile(.$RT,
                                      probs=quantile_points,
                                      names=FALSE)
                        )
             )
   data <- ungroup(data)
   data
}

quantile_points <- seq(.01,1,length.out = 100)
# 
# quantiles_correct <- IV_sub %>%
#   filter(final_acc == 1,
#          !is.na(RT)) %>%
#   calculate_quantiles(quantile_points) %>%
#   left_join(y = IV[IV$final_acc==1,
#                    c("group","practice","OCpractice","mean_p")],
#             by = c("group","practice","OCpractice")) %>%
#   mutate(probability = probability * mean_p) %>%
#   select(-mean_p)
# 
# practice_labels <- c(N.N = "Baseline",
#                      N.S = "Study, Other Cue",
#                      S.N = "Study, Same Cue",
#                      N.T = "Test, Other Cue",
#                      T.N = "Test, Same Cue")
# 
# capitalize <- function(string) {
#   substr(string, 1, 1) <- toupper(substr(string, 1, 1))
#   string
# }
# 
# quantile_plot <- ggplot(quantiles_correct,
#                         aes(x=RT,
#                             y=probability,
#                             color = interaction(practice, OCpractice)
#                             )
#                         ) +
#   geom_line(size=.75) +
#   facet_grid(.~ group,
#              labeller = labeller(.default = capitalize)
#              ) + 
#   scale_color_discrete(name="Condition",
#                        breaks = c("N.N","N.S","N.T","S.N","T.N"),
#                        labels = practice_labels) +
#   scale_x_continuous(breaks = 0:6,
#                      limits=c(0,6)) + 
#   theme_grey(base_size = 16)
# print(quantile_plot)
```

### Pooled Quantiles
Quantiles are calculated using all observed RT's within a condition, pooled over subjects. They conditioned based on the observed accuracy in that condition. Thus, the quantile curves terminate at the observed accuracy for a particular condition, rather than 1.

```{r pooled_quantiles, fig.height=8,fig.width = 11}
# IV_acc_pooled <- LB4L2_final %>%
#   group_by(group,practice,OCpractice) %>%
#   summarise(acc=mean(acc))
#   
# pooled_quantiles_correct <- LB4L2_final %>%
#   filter(acc == 1) %>%
#   calculate_quantiles(quantile_points) %>%
#   left_join(y = IV_acc_pooled,
#             by = c("group","practice","OCpractice")) %>%
#   mutate(probability = probability * acc) %>%
#   select(-acc)
# 
# quantile_plot %+% pooled_quantiles_correct
```
